\documentclass{exam}
\begin{document}
FIRST QUIZ: CS4472A Tuesday, 3 October 2017, 7:10pm, Room MC17\newline
\newline
\newline
\newline
NAME AS APPEARS ON STUDENT ID:\newline
\newline
STUDENT ID NUMBER:\newline
\newline
UWO/CONFLUENCE USER NAME:\newline
\newline
REMINDERS:
\begin{enumerate}
\item (from course outline) The quiz will be closed book, closed notes, with no electronic devices allowed, with particular reference to any electronic devices that are capable of communication and/or storing information.
\item Write neatly.  If the marker can't read it, it is wrong.
\item This exam shouldn't take long to write.  On the other hand, time will pass.  It is a 30 minute quiz with 20 questions.  If you complete a question every  minute you will still have 10 minutes at the end to double check that everything is in order.
\item While you are not allowed to open the exam booklet until the proctor says you can, you can fill out the information on the cover page.  You should also get out your student id and make sure your pencils and pens are in order.  If you need to get something out of your jacket or knapsack once the exam has started, raise your hand and wait til a proctor comes to you to oversee the matter.
\end{enumerate}
\newpage
\begin{enumerate}
\item Testing is generally about finding errors that have already been made.  This course also covers the topic of ANSWER, which is about trying to prevent errors from being made in the first place.\newline
ANSWER=
\item The scripts that were designed to aid the practice process assume that you will be uploading a copy of your work to BitBucket every time you ANSWER\newline
ANSWER=
\item The kind of testing we do to make sure that when we change a program we do not break something that used to work is called ANSWER\newline
ANSWER=
\item The per cent of the total mark allocated for all the practice reviews is ANSWER\newline
ANSWER=
\item It is easy to make up test inputs, but it can be tricky to know what the right output for a given input should be.  This is refered to as the ANSWER problem\newline
ANSWER=
\item The number of quizzes CS4472 will have this semester is ANSWER\newline
ANSWER=
\item The per cent of the total mark allocated for all the quizzes is ANSWER\newline
ANSWER=
\item An important concept we will look at related to the question of when has one done enough testing is ANSWER\newline
ANSWER=
\item To illustrate the relation between testing and software design, we will look at the programming technique ANSWER\newline
ANSWER=
\item The first testing framework for Ruby that we are looking at is called ANSWER\newline
ANSWER=
\item The protocols for practice expect that the longest amount of time that you will practice before recording a note is ANSWER\newline
ANSWER=
\item The per cent of the total mark allocated for all the weekly practices is ANSWER\newline
ANSWER=
\item The total amount of practice time you can get credit for during a practice week is ANSWER\newline
ANSWER=
\item A main theme behind the practice technique advocated in this class is that in order to improve your programming, ANSWER\newline
ANSWER=
\item The four phases of testing (according to Whittaker) are: 1) modeling the software environment, 2) selecting test cases, 3) running and checking test cases, and 4) ANSWER\newline
ANSWER=
\item Using combinatorial testing, if I have 10 binary inputs, I only need to use ANSWER test cases (each a setting of each of the 10 inputs) to expect to find 98 per cent of the errors in the program.\newline
ANSWER=
\item Structural testing is another name for ANSWER\newline
ANSWER=
\item The number of weekly practices that CS4472 will have this semester is ANSWER\newline
ANSWER=
\item Although we often think of programs as taking inputs and producing outputs, a higher level view of what is going on is to think of the programs as ANSWER about how to take inputs and produce outputs.\newline
ANSWER=
\item A common piece of information for people interested in programmer productivity to track is ANSWER\newline
ANSWER=
\item The first tool for checking code quality for programs written in Ruby is ANSWER, which is described as a code smell detector.\newline
ANSWER=
\item The testing technique called boundary value partition starts with the notion of breaking the space of inputs into ANSWER\newline
ANSWER=
\item The ANSWER is a method developed by Watt S. Humphrey to help individuals improve their programming skills based on existing methods that had been developed to help organizations improve their product development capabilities.\newline
ANSWER=
\item The practice technique advocated in this class is a modification of the ANSWER\newline
ANSWER=
\item The number of practice reviews that CS4472 will have this semester is ANSWER\newline
ANSWER=
\end{enumerate}
\newpage
\begin{verbatim}
exam_database_file= examdatabase.json
exam_format= latex
dump_database= false
line_width= 72
question_count= 173
create_exam= false
answer_key= true
sample_seed= 222
shuffle_seed= 2345
["C1", "C2", "C3"]
["C1", "C2", "C3"]
\end{verbatim}
\begin{enumerate}
\item quality assurance
\item record a note about your practice progress
\item regression testing
\item 49
\item Oracle
\item 3
\item 21
\item \begin{itemize}
\item coverage
\item mutation
\end{itemize}
\item test driven development
\item minitest
\item 30 minutes
\item 30
\item 3 hours
\item you need data about your past programming
\item checking how well the testing is going
\item 13
\item \begin{itemize}
\item code-based testing
\item white-box testing
\end{itemize}
\item 10
\item encode knowledge
\item \begin{itemize}
\item time spent
\item number of lines of code written
\item number of defects found
\end{itemize}
\item reek
\item regions of interest
\item Personal Software Process
\item Personal Software Process
\item 4
\end{enumerate}
\end{document}
